\documentclass[11pt, a4paper, sans]{moderncv}

%% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.75]{geometry}
\geometry{top=2.5cm, bottom=2.5cm}

\usepackage{fancyhdr}
\pagestyle{fancy}
%\lhead{\textbf{U-M ID: 98197295}}

%% Personal data
\firstname{Zhenyuan}
\familyname{Zhang}
\title{Resume}
%\address{Room 1601, No.12, 665 Dongchangzhi Road}{Shanghai, 200080}
\address{5C, 1811 Willowtree Ln, Ann Arbor}{Michigan, 48105}
\mobile{+1~(734)~882~3816}
\email{cryscan@umich.edu}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle
	
\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{ \textit{Grade} }{Description}  % arguments 3 to 6 can be left empty
\cventry{Sep. 2019 -- Present}
{Bachelor of Science}
{University of Michigan}
{Ann Arbor}
{GPA 4.0 out of 4.0}
{Major in Computer Science}

\cventry{Sep. 2017 -- Present}
{Bachelor of Science}
{University of Michigan -- Shanghai Jiao Tong University Joint Institute}
{Shanghai}
{GPA 3.6 out of 4.0}
{Major in Electronic and Computer Engineering}

\section{Experience}
\cventry{Sep. 2019 -- Dec. 2019}
{Unity Programmer}
{WolverineSoft Studio Long Term Project}
{}{}
{A top-down 2D twin-stick shooter made by the University of Michigan's video game development club
\begin{itemize}
\item Worked over the course of one semester with a team of 30 developers
\item Implemented the projectile system
\end{itemize}}

\cventry{Nov. 2018 -- Apr. 2019}{Student}{Undergraduate Research Program}{}{}
{\cvitem{Spring 2019}{Proof of Convergence of Quantile Q-learning}
A variant of Q-learning that does not need quantified reward, but relative orders instead
\begin{itemize}
\item Proved with stochastic approximation technique
\end{itemize}}
{\cvitem{Fall 2018}{Evaluation of Algorithms for Deep Reinforcement Learning}
\begin{itemize}
\item Set up an unified environment that integrates different algorithms and scenarios
\item Implemented state-of-the-art reinforcement learning algorithms (\texttt{PPO}, \texttt{DDPG})
\item Implemented a benchmarking procedure for algorithm evaluating
\end{itemize}
}

\cventry{Sep. 2018 -- Aug. 2019}
{Member}
{Student Science and Technology Innovation Association}
{}{}
{A students' association for sharing advanced technologies
\begin{itemize}
	\item Held workshops on computer graphics (\texttt{OpenGL}, rendering pipeline, transforms in 3D)
\end{itemize}}

\section{Activities and Honors}
\cventry{Mar. 2018 -- Apr. 2018}
{Team Leader}
{The 10th SJTU Mechanical Innovation Competition for Freshmen}
{}{Entered the second round}
{A college-level competition in robot designing}

\section{Computer Skills}
\cvitem{Programming Languages}{
\begin{itemize}
	\item \cvitem{\texttt{C++}}{Have knowledge and skill of RAII, multi-threading and template metaprogramming}
	\item \cvitem{\texttt{Rust}}{Understand ownership, lifetime and type traits}
	\item \cvitem{\texttt{Python}}{Use for daily scripting}
\end{itemize}}
\cvitem{Game Engine}{\texttt{Unity}}
\cvitem{Asset Creating}{\texttt{Blender} for 3D modeling and animating}

\end{document}