\documentclass[10pt, a4paper, sans]{moderncv}

%% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.75]{geometry}
\geometry{top=2.0cm, bottom=2.0cm}

\usepackage{fancyhdr}
\pagestyle{fancy}
% \lhead{\textbf{Program: Computer Science and Engineering Ph.D. \\ U-M ID: 98197295}}

%% Personal data
\firstname{Zhenyuan}
\familyname{Zhang}
\title{}
%\address{Room 1601, No.12, 665 Dongchangzhi Road}{Shanghai, 200080}
\address{5C, 1811 Willowtree Ln, Ann Arbor}{Michigan, 48105}
\mobile{+1~(734)~882~3816}
\email{cryscan@umich.edu}
\homepage{cryscan.github.io/profile}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{ \textit{Grade} }{Description}  % arguments 3 to 6 can be left empty
\cventry{Sep. 2021 -- May 2023}
{Master of Science in Computer Science}
{University of Michigan}
{Ann Arbor}
{}
{\cvitem{Core courses}{Parallel Computing, Category Theory, Motion Robotics}}

\cventry{Sep. 2019 -- May 2021}
{Bachelor of Science in Computer Science}
{University of Michigan}
{Ann Arbor}
{GPA 3.8 out of 4.0}
{\cvitem{Core courses}{Computer Architecture, Data Structures and Algorithms, Operating Systems, Compiler Construction, Game Development, Robotics Kinematics and Dynamics}}

\cventry{Sep. 2017 -- Aug. 2021}
{Bachelor of Science in Electronic and Computer Engineering}
{University of Michigan -- Shanghai Jiao Tong University Joint Institute}
{Shanghai}
{GPA 3.6 out of 4.0}
{\cvitem{Core courses}{Engineering Probabilistic Methods, Differential Equations, Linear Algebra, Discrete Mathmetics}}

\section{Experience}
\cventry{Jan. 2022 - Feb. 2022}
{Programmer}
{Voxel Cone Tracing Global Illumination}{}{}
{
	An extension for the bevy game engine which implements global illumination using voxel cone tracing
	\begin{itemize}
		\item Built with WebGPU, a modern GPU rendering and computing API
		\item Developed pipelines for voxelizing the scene, generating mipmaps and tracing the voxel data
		\item Published as a 3rd-party plugin to \texttt{crates.io}
	\end{itemize}
}

\cventry{Dec. 2021 - Jan. 2022}
{Designer and Programmer}
{Parallel $A^\star$ Search on GPU}{}{}
{
	A research project on paralleling $A^\star$ searching algorithm on a GPU
	\begin{itemize}
		\item Implemented heap, hashtable and memory pool on GPUs in \texttt{CUDA} and \texttt{C++}
		\item Got an approximately 10x speedup on Quadro RTX 4000 than the single-threaded version on i7 8700
	\end{itemize}
}

\cventry{Jan. 2021 -- Apr. 2021}
{Leader}
{Procedural Animation Project}
{}{}
{
	A research project seeks to introduce methods of motion synthesis in robotics into animation systems
	\begin{itemize}
		\item Wrote a differentiable physics simulation with hard contacts
		\item Generated the physically-correct trajectory for characters offline
		\item Applied to real-time game-like applications using motion matching and IK
	\end{itemize}
}

\cventry{Oct. 2020 -- Dec. 2020}
{Designer and Programmer}
{Undergraduate Game Development}
{}{}
{A game project done by a team of four in one semester with \texttt{Unity Engine}
	\begin{itemize}
		\item Designed core mechanism focused on planning and executing
		\item Designed the code architecture based on event channels (pub-sub design pattern)
		\item Implemented enemy AI with complex but reasonable behavior using \texttt{Goal Oriented Action Planning}
	\end{itemize}
}

\cventry{May 2020 -- Feb. 2021}
{Student Researcher}
{Research in ARM Lab on Trap Aware Model Predictive Control}
{}{}
{
	An online model-based controller for escaping traps in novel environments
	\begin{itemize}
		\item Implemented baseline based on \texttt{Guided Policy Search} in \texttt{Python}
		\item Implemented baseline based on \texttt{Soft Actor-Critic} in \texttt{Python}
	\end{itemize}
}

% \cventry{June. 2020 -- August. 2020}
% {Unity Programmer}
% {WolverineSoft Studio Game Project}
% {}{}
% {A 3D first-person stealth horror game where the player must traverse through a castle avoiding horrible monsters
% 	\begin{itemize}
% 		\item Worked over the course of one semester with a team of 30 developers
% 		\item Created enemy animations using trajectory optimization
% 		\item Implemented an easy-to-use interacting system
% 		\item Implemented dialogue system for narrative purpose
% 	\end{itemize}
% }

% \cventry{Nov. 2018 -- Apr. 2019}
% {Student Researcher}
% {Undergraduate Research Program}
% {}{}
% {
% 	Evaluation of Algorithms for Deep Reinforcement Learning
% 	\begin{itemize}
% 		\item Set up an unified environment that integrates different algorithms and scenarios
% 		\item Implemented reinforcement learning algorithms including \texttt{PPO} and \texttt{DDPG} in \texttt{TensorFlow}
% 		\item Implemented a benchmarking procedure for algorithm evaluating
% 	\end{itemize}
% }

% \section{Activities and Honors}
% \cventry{Mar. 2018 -- Apr. 2018}
% {Team Leader}
% {The 10th SJTU Mechanical Innovation Competition for Freshmen}
% {}{Entered the second round}
% {A college-level competition in robot designing}

\section{Skills}
\cvitem{Programming Languages}{
	\begin{itemize}
		\item \cvitem{\texttt{C++}}{Have good coding style; Have experience in multiple projects}
		\item \cvitem{\texttt{Rust}}{Understand ownership, lifetime and traits; Have project experience}
	\end{itemize}}
\cvitem{Game Engines}{\texttt{Unity}, \texttt{Bevy} (Written in \texttt{Rust})}
\cvitem{Others}{\texttt{Git}, \texttt{Jira}, \texttt{Blender}}

\end{document}